### 2023-01-18 paper.tex
Checked references

	Apart from the improvements to the repository itself, the next steps involve actually using the repository for applying code mining algorithms, as intended. Upcoming research using this repository should aim at using the enhanced information in the Smart Contract Repository towards achieving the research aims mentioned in this paper---primarily in the fields of gas consumption, machine learning and qualitative and quantitative analysis of the smart contracts.
	\bibliographystyle{IEEEtran}
	\bibliography{biblio}

\end{document}

>>>>

	Apart from the improvements to the repository itself, the next steps involve actually using the repository for applying code mining algorithms, as intended. Upcoming research using this repository should aim at using the enhanced information in the Smart Contract Repository towards achieving the research aims mentioned in this paper---primarily in the fields of gas consumption, machine learning and qualitative and quantitative analysis of the smart contracts.

	\todo{W.r.t. the references: Please make sure that the style/layout is unified. E.g., either abbreviate all journal names using the same rules, or abbreviated none. Also make sure that Arxiv papers (like 15--19; 15 is the correct form) are layouted the same way. Check also for all other Arxiv papers! For the GASOL and Manticore papers, better cite the peer-reviewed versions, not the Arxiv ones (actually, check for all Arxiv papers as well if there is a peer-reviewed version available; if yes, replace it). The paper by Morabito is missing editors and booktitle. PAper 32 is missing the authors. PAper 60 is missing quite a lot of information. The Soda-Paper is pretty much missing everything. The Smart-Corpus paper can be found twice in the references, make sure that it shows up only once (and there are no missing references!). In general, to unify and complete your references from the very beginning}

	\bibliographystyle{IEEEtran}
	\bibliography{biblio}	
\end{document}
